SunPy - Python for Solar Physics

### 2014-01-20 1-Introduction.tex
More post-merge changes

While SSW is open-source and freely available, the IDL core is not. In addition, the development
of SolarSoft is neither open nor transparent to the public. Also IDL is fairly limited in 
its ability to interact with other languages. One of SunPy's key aims is to 
provide a free and modern alternative to the SolarSoft (gen) library. This is made possible
by the recent rise of the scientific Python community. Python is general purpose 
high-level programming language. It is free to use, cross-platform, and has a strong
emphasis on readability a concept which is well-aligned with the scientific endeavor.
Python has a very large user community which extends far outside of the solar physics
or astronomy communities. It is very extensible with C, C++, Fortran or even IDL. It is 
easy to learn. Many books and on-line documentation is available. For example at the time
of this writing a search on Amazon for books on IDL programming generated 189 results while a search
for Python yielded 1,788 results. Additionally, students may already have learned Python during their 
undergraduate which means that research projects can begin quickly without the need for 
the student to learn a new (and relatively niche) language. Finally, knowledge of Python is a skill which is useful
and well compensated outside of the scientific community (average salary of \$110k in Washington DC area according
to indeed.com at the time of writing). Finally, the astronomy community has begun to
move away from IDL to Python. For all of these reasons, Python is an ideal platform for
the generation of solar physics data analysis environment.

>>>>

While SSW is open-source and freely available, the IDL core is not. In 
addition, the development of SolarSoft is neither open nor transparent to the 
public. Also IDL is fairly limited in its ability to interact with other 
languages. One of SunPy's key aims is to provide a free and modern alternative 
to the SolarSoft (gen) library. This is made possible by the recent rise of the 
scientific Python community. Python is general purpose high-level programming 
language. It is free to use, cross-platform, and has a strong emphasis on 
readability a concept which is well-aligned with the scientific endeavor.
Python has a very large user community which extends far outside of the solar 
physics or astronomy communities. It is very extensible with C, C++, Fortran or 
even IDL. It is easy to learn. Many books and on-line documentation is 
available. For example at the time of this writing a search on Amazon for books 
on IDL programming generated $189$ results while a search for Python yielded 
$1,788$ results. Additionally, students may already have learned Python during 
their  undergraduate which means that research projects can begin quickly 
without the need for the student to learn a new (and relatively niche) 
language. Finally, knowledge of Python is a skill which is useful and well 
compensated outside of the scientific community (average salary of \$110k in 
Washington DC area according to indeed.com at the time of writing). Finally, 
the astronomy community has begun to move away from IDL to Python. For all of 
these reasons, Python is an ideal platform for the generation of solar physics 
data analysis environment.

### 2014-01-20 3-4-Helioviewer.tex
More post-merge changes

SunPy provides the ability to download images from Helioviewer Project
servers.  The aim of the Helioviewer Project is to enable the
exploration of solar and heliospheric data from multiple data sources
(such as instrumentation and feature/event catalogs) via easy-to-use
visual interfaces.  The primary data provided by the Helioviewer
Project are images in the JPEG2000 format (for further details on the
Helioviewer Project see \cite{}\footnote{SunPy is used in Helioviewer
  production servers to manage the download and ingestion of JPEG2000
  files from remote servers.}.)  The JPEG2000 files are typically
highly compressed compared to the source FITS files they are generated
from, and so can be a used as a shortcut to visualize large amounts of
data from multiple sources.

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 6, "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],[SOHO,LASCO,C2,white-light,1,100]", x0=0, y0=0, width=768, height=768)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example.eps}
\caption{Acquisition of a PNG image composed from data from three
  separate sources.}
\label{code:hv:overlaid}
\end{listing}

@@

%
% Helioviewer article citation
%
%@article{Muller:2009:JVL:2220073.2220164,
% author = {Muller, D. and Fleck, B. and Dimitoglou, G. and Caplins, B. W. and Amadigwe, D. E. and Ortiz, J. P.G. and Wamsler, B. and Alexanderian, A. and Hughitt, V. K. and Ireland, J.},
% title = {JHelioviewer: Visualizing Large Sets of Solar Images Using JPEG 2000},
% journal = {Computing in Science and Engg.},
% issue_date = {September 2009},
% volume = {11},
% number = {5},
% month = sep,
% year = {2009},
% issn = {1521-9615},
% pages = {38--47},
% numpages = {10},
% url = {http://dx.doi.org/10.1109/MCSE.2009.142},
% doi = {10.1109/MCSE.2009.142},
% acmid = {2220164},
% publisher = {IEEE Educational Activities Department},
% address = {Piscataway, NJ, USA},
% keywords = {data visualization},
%}

>>>>

SunPy provides the ability to download images from Helioviewer Project
servers.  The aim of the Helioviewer Project is to enable the
exploration of solar and heliospheric data from multiple data sources
(such as instrumentation and feature/event catalogs) via easy-to-use
visual interfaces.  The primary data provided by the Helioviewer
Project are images in the JPEG2000 format (for further details on the
Helioviewer Project see \cite{muller2009}\footnote{SunPy is used in Helioviewer 
production servers to manage the download and ingestion of JPEG2000
files from remote servers.}.)  The JPEG2000 files are typically
highly compressed compared to the source FITS files they are generated
from, and so can be a used as a shortcut to visualize large amounts of
data from multiple sources.

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 6, 
"[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50], \
[SOHO,LASCO,C2,white-light,1,100]", x0=0, y0=0, width=768, height=768)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example.eps}
\caption{Acquisition of a PNG image composed from data from three
  separate sources.}
\label{code:hv:overlaid}
\end{listing}

@@
